Verifying Demonstrations

### 2018-11-16 paper/intro.tex

In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.

>>>>

In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.

### 2018-11-16 paper/verifiability-analysis.tex

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \PRIVO, we have several attributes that must be verifiable: the time of 
creation (\ie, temporal eligibility, \cref{TemporallyRelated}), the physical 
location of \(\sk_P\) at creation (\ie, spatial eligibility, 
\cref{SpatiallyRelated}), recognition of two proofs originating from the same 
person (\ie, one-proof-per-person eligibility, \cref{CountOnce}) and that the 
proof is indeed designated for the event (\ie, designated-event eligibility, 
\cref{DesignatedEvent}).
We will now analyze these properties.

>>>>

\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
In \CROCUS, we have several attributes that must be verifiable: the time of 
creation (\ie, temporal eligibility, \cref{TemporallyRelated}), the physical 
location of \(\sk_P\) at creation (\ie, spatial eligibility, 
\cref{SpatiallyRelated}), recognition of two proofs originating from the same 
person (\ie, one-proof-per-person eligibility, \cref{CountOnce}) and that the 
proof is indeed designated for the event (\ie, designated-event eligibility, 
\cref{DesignatedEvent}).
We will now analyze these properties.
